---
title: "NFL Week 10"
author: "MAJ Daniel Baller"
date: "8/27/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = F)
library(tidyverse)
library(dplyr)
library(ggplot2)
library(data.table)
library(formattable)
library(ggpubr)
library(ggrepel)
week_1 = read_csv("NFL Week 1.csv")
week_2 = read_csv("NFL Week 2.csv")
week_3 = read_csv("NFL Week 3.csv")
week_4 = read_csv("NFL Week 4.csv")
week_5 = read_csv("NFL Week 5.csv")
week_6 = read_csv("NFL Week 6.csv")
week_7 = read_csv("NFL Week 7.csv")
week_8 = read_csv("NFL Week 8.csv")
week_9 = read_csv("NFL Week 9.csv")
data = read_csv("NFL Week 10.csv") # Update
cadet_wk1 = read_csv("NFL Week 1 Prediction MA206.csv")
cadet_wk2 = read_csv("NFL Week 2 MA206.csv")
cadet_wk3 = read_csv("NFL Week 3 MA206.csv")
cadet_wk4 = read_csv("NFL Week 4 MA206.csv")
cadet_wk5 = read_csv("NFL Week 5 MA206.csv")
cadet_wk6 = read_csv("NFL Week 6 MA206.csv")
cadet_wk7 = read_csv("NFL Week 7 MA206.csv") 
cadet_wk8 = read_csv("NFL Week 8 MA206.csv") 
cadet_wk9 = read_csv("NFL Week 9 MA206.csv") 
cadet_wk10 = read_csv("NFL Week 10 MA206.csv") # Update
```

```{r games, include=FALSE}
#basic info

n = 13 #number of games this week
wk1_n = 16 # number of games in week 1
wk2_n = 16 # number of games in week 2
wk3_n = 16 # number of games in week 3
wk4_n = 15 # number of games in week 4
wk5_n = 15 # number of games in week 5
wk6_n = 13 # number of games in week 6
wk7_n = 14 # number of games in week 7
wk8_n = 15 # number of games in week 8
wk9_n = 14 # number of games in week 8
g1_n = 16 # number of group picks in week 1
g2_n = 16 # number of group picks in week 2
g3_n = 16 # number of group picks in week 3
g4_n = 15 # number of group picks in week 4
g5_n = 13 # number of group picks in week 5
g6_n = 12 # number of group picks in week 6
g7_n = 14 # number of group picks in week 7
g8_n = 15 # number of group picks in week 8
g9_n = 14 # number of group picks in week 8
wk1_wins = 10 #number of wins in week 1
wk2_wins = 10 #number of wins in week 2
wk3_wins = 12 #number of wins in week 3
wk4_wins = 8 #number of wins in week 4 
wk5_wins = 8 #number of wins in week 5 
wk6_wins = 6 #number of wins in week 6 
wk7_wins = 9 #number of wins in week 7 
wk8_wins = 13 #number of wins in week 8 
wk9_wins = 7 #number of wins in week 9 #update this
wk1_combined_wins = 12 # number of combined wins in week 1
wk2_combined_wins = 10 # number of combined wins in week 2
wk3_combined_wins = 10 # number of combined wins in week 3 
wk4_combined_wins = 8 # number of combined wins in week 4 
wk5_combined_wins = 9 # number of combined wins in week 5 
wk6_combined_wins = 7 # number of combined wins in week 6 
wk7_combined_wins = 10 # number of combined wins in week 7 
wk8_combined_wins = 13 # number of combined wins in week 8
wk9_combined_wins = 7 # number of combined wins in week 9 # update this

# who actually won
winners = c("Oakland Raiders","Baltimore Ravens","Cleveland Browns","Chicago Bears","New York Jets","Tennessee Titans","Tampa Bay Buccaneers","Atlanta Falcons","Indianapolis Colts","Los Angeles Rams","Green Bay Packers","Minnesota Vikings","Seattle Seahawks")

CBSsports = c("Oakland Raiders","Baltimore Ravens","Buffalo Bills","Detroit Lions","New York Giants","Kansas City Chiefs","Tampa Bay Buccaneers","New Orleans Saints","Indianapolis Colts","Los Angeles Rams","Green Bay Packers","Minnesota Vikings","Seattle Seahawks")

wk1_winners = c("Green Bay Packers","Minnesota Vikings","Baltimore Ravens","Buffalo Bills","Kansas City Chiefs","Los Angeles Rams","Tennessee Titans","Philadelphia Eagles","Seattle Seahawks","Los Angeles Chargers","TIE","Dallas Cowboys","San Francisco 49ers","New England Patriots","New Orleans Saints","Oakland Raiders")

wk2_winners = c("Tampa Bay Buccaneers","Baltimore Ravens","Dallas Cowboys","Indianapolis Colts","Seattle Seahawks","Buffalo Bills","San Fransisco 49ers","Detroit Lions","Green Bay Packers","Houston Texans","New England Patriots","Kansas City Chiefs","Los Angeles Rams","Chicago Bears","Atlanta Falcons","Cleveland Browns")

wk3_winners = c("Jacksonville Jaguars","Buffalo Bills","Detroit Lions","New England Patriots","Minnesota Vikings","Kansas City Chiefs","Indianapolis Colts","Green Bay Packers","Dallas Cowboys","New York Giants","Carolina Panthers","San Francisco 49ers","New Orleans Saints","Houston Texans","Los Angeles Rams","Chicago Bears") 

wk4_winners = c("Philadelphia Eagles","Tennessee Titans","New York Giants","Los Angeles Chargers","Oakland Raiders","Carolina Panthers","Kansas City Chiefs","Cleveland Browns","New England Patriots","Tampa Bay Buccaneers","Seattle Seahawks","Chicago Bears","Jacksonville Jaguars","New Orleans Saints","Pittsburgh Steelers")

wk5_winners = c("Seattle Seahawks","Carolina Panthers","New England Patriots","Buffalo Bills","Baltimore Ravens","Arizona Cardinals","Houston Texans","New Orleans Saints","Minnesota Vikings","Oakland Raiders","Philadelphia Eagles","Denver Broncos","Green Bay Packers","Indianapolis Colts","San Francisco 49ers") 

wk6_winners = c("New England Patriots","Carolina Panthers","Washington Redskins","Minnesota Vikings","Houston Texans","New Orleans Saints","Seattle Seahawks","San Francisco 49ers","Arizona Cardinals","New York Jets","Denver Broncos","Pittsburgh Steelers","Green Bay Packers") 

wk7_winners = c("Kansas City Chiefs","Buffalo Bills","Jacksonville Jaguars","Minnesota Vikings","Green Bay Packers","Los Angeles Rams","Indianapolis Colts","San Francisco 49ers","Arizona Cardinals","Tennessee Titans","New Orleans Saints","Baltimore Ravens","Dallas Cowboys","New England Patriots")

wk8_winners = c("Minnesota Vikings","Seattle Seahawks","Indianapolis Colts","Tennessee Titans","New Orleans Saints","Los Angeles Rams","Philadelphia Eagles","Los Angeles Chargers","Detroit Lions","Jacksonville Jaguars","San Francisco 49ers","Houston Texans","New England Patriots","Green Bay Packers","Pittsburgh Steelers")

wk9_winners = c("San Francisco 49ers","Houston Texans", "Philadelphia Eagles","Pittsburgh Steelers","Miami Dolphins","Kansas City Chiefs","Carolina Panthers","Buffalo Bills","Seattle Seahawks","Oakland Raiders","Los Angeles Chargers","Denver Broncos","Baltimore Ravens","Dallas Cowboys") # update this

#wk1_CBSsports = c("Green Bay Packers","Atlanta Falcons","Miami Dolphins","New York Jets","Kansas City Chiefs","Carolina Panthers","Cleveland Browns","Philadelphia Eagles","Seattle Seahawks","Indianapolis Colts","Arizona Cardinals","Dallas Cowboys","Tampa Bay Buccaneers","Pittsburgh Steelers","New Orleans Saints","Oakland Raiders")

#wk2_CBSsports = c("Carolina Panthers","Baltimore Ravens","Dallas Cowboys","Indianapolis Colts","Seattle Seahawks","Buffalo Bills","Cincinnati Bengals","Los Angeles Chargers","Green Bay Packers","Houston Texans","New England Patriots","Kansas City Chiefs","Los Angeles Rams","Chicago Bears","Philadelphia Eagles","Cleveland Browns")

#wk3_CBSsports = c("Jacksonville Jaguars","Buffalo Bills","Philidelphia Eagles","New England Patriots","Minnesota Vikings","Baltimore Ravens","Atlanta Falcons","Green Bay Packers","Dallas Cowboys","Tampa Bay Buccaneers","Carolina Panthers","San Francisco 49ers","Seattle Seahawks","Los Angeles Chargers","Los Angeles Rams","Chicago Bears") 

#wk4_CBSsports = c("Green Bay Packers","Atlanta Falcons","Washington Redskins","Los Angeles Chargers","Indianapolis Colts","Carolina Panthers","Kansas City Chiefs","Baltimore Ravens","New England Patriots","Los Angeles Rams","Seattle Seahawks","Chicago Bears","Jacksonville Jaguars","Dallas Cowboys","Pittsburgh Steelers")

#Wk5_CBSsports = c("Seattle Seahawks","Jacksonville Jaguars","New England Patriots","Tennessee Titans","Baltimore Ravens","Cincinnati Bangals","Houston Texans","Tamps Bay Buccaneers","Minnesota Vikings","Chicago Bears","Philadelphia Eagles","Los Angeles Chargers","Dallas Cowboys","Kansas City Chiefs","Cleveland Browns")

#wk6_CBSsports = c("New England Patriots","Tampa Bay Buccaneers","Washington Redskins","Philadelphia Eagles","Kansas City Chiefs","New Orleans Saints","Seattle Seahawks","San Francisco 49ers","Atlanta Falcons","Dallas Cowboys","Tennessee Titans","Los Angeles Chargers","Green Bay Packers")

#wk7_CBSsports = c("Denver Broncos","Buffalo Bills", "Jacksonville Jaguars","Minnesota Vikings","Green Bay Packers","Los Angeles Rams","Houston Texans","San Francisco 49ers","Arizona Cardinals","Los Angeles Chargers","New Orleans Saints","Baltimore Ravens","Philadelphia Eagless","New England Patriots")

#wk8_CBSsports = c("Minnesota Vikings","Seattle Seahawks","Indianapolis Colts","Tampa Bay Buccaneers","New Orleans Saints","Los Angeles Rams","Philadelphia Eagles","Los Angeles Chargers","Detroit Lions","Jacksonville Jaguars","San Francisco 49ers","Houston Texans","New England Patriots","Green Bay Packers","Pittsburgh Steelers")

#wk9_CBSsports = c("San Francisco 49ers","Houston Texans", "Philadelphia Eagles","Indianapolis Colts","New York Jets","Minnesota Vikings","Carolina Panthers","Buffalo Bills","Seattle Seahawks","Oakland Raiders","Green Bay Packers","Cleveland Browns","Baltimore Ravens","Dallas Cowboys")

experts = ifelse(winners == CBSsports, 1, 0)
CBS = round(sum(experts)/n,4)
```

## Group Predictions

```{r Group Predictions, include=FALSE}
games = data %>% janitor::clean_names() %>%
  select(starts_with("game"))  #Creating the set of just games

# creating a table of predictions and votes for and against the prediction
pred_table = data.frame(Game=colnames(games), 
                        t(sapply(games, # apply following function to each column
                                 function(x) {
                                   t_x <- sort(table(x), decreasing=TRUE) # get the frequencies and sort them in decreasing order
                                   list(Prediction=names(t_x)[1], # name of the value with highest frequency
                                        votes_for=t_x[1], # highest frequency
                                        votes_against=t_x[2]) # Lowest Freq
                                 })))

#establish vectors for precictions and votes for and against
pred_table = pred_table %>% 
  mutate(votes_against = ifelse(is.na(pred_table$votes_against)==T, 0, as.integer(pred_table$votes_against))) # turning NA in votes against column into 0
pred = ifelse(as.numeric(pred_table$votes_for) == as.numeric(pred_table$votes_against), "Tie", as.character(pred_table$Prediction)) #choosing prediction or tie if no prediction
#votes_for = ifelse(is.na(pred_table$votes_for)==T, 0, as.integer(pred_table$votes_for))
votes_for = as.integer(pred_table$votes_for)
votes_against = as.integer(pred_table$votes_against)

results = tibble(Game = 1:length(games)) %>% 
  add_column(Prediction = pred) %>%
  add_column(Winners = winners) %>%
  mutate(Correct = ifelse(Prediction =="Tie", "--", ifelse(Prediction == Winners, "Yes", "No"))) %>%
  mutate(Correct_Votes = ifelse(Prediction == winners, votes_for, ifelse(winners == "TIE", 0, votes_against))) %>%
  mutate(Percentage_For = round(Correct_Votes/dim(data)[1],4)) %>%
  rename("Correct Votes" = Correct_Votes) %>%
  rename("Correct Percent" = Percentage_For)
results
```

```{r displaying group results, echo=FALSE}
# formating for color of table
improvement_formatter2 <- 
  formatter("span", 
            style = x ~ style(
              font.weight = "bold", 
              color = ifelse(x == "Yes", "green", ifelse(x =="No", "red", "black"))))


# Creatign Group Prediction table            
formattable(results, 
            align =c("c","c","c"), 
            list(
              `Indicator Name` = formatter("span", 
                                style = ~ style(color = "grey",font.weight = "bold")),
                                "Correct" = improvement_formatter2))

# Printing the weekly and season win percentage            
correct_count = count(results, Correct)
weekly_win_percentage = round(correct_count$n[which(correct_count$Correct == "Yes")]/(n-ifelse(identical(correct_count$n[which(correct_count$Correct == "--")], integer(0))==TRUE, 0, correct_count$n[which(correct_count$Correct == "--")])),4)
group_games = (n-ifelse(identical(correct_count$n[which(correct_count$Correct == "--")], integer(0))==TRUE, 0, correct_count$n[which(correct_count$Correct == "--")]))
season_games = group_games+g1_n+g2_n+g3_n+g4_n+g5_n+g6_n+g7_n+g8_n+g9_n
season_wins  = wk1_wins+wk2_wins+wk3_wins+wk4_wins+wk5_wins+wk6_wins+wk7_wins+wk8_wins+wk9_wins+
  correct_count$n[which(correct_count$Correct == "Yes")]
season_win_percentage = round(season_wins/(season_games),4)
Total = dim(data)[1]
```
 `r paste("Our win percentage for the week is", weekly_win_percentage, sep = " ") `
 
 `r paste("CBS Sports win percentage for the week is", CBS, sep = " ") `
 
 `r paste("Our season win percentage so far is", season_win_percentage, sep = " ") `
 
 `r paste("Games picked this season", season_games, sep = " ") `
 
 `r paste("Correct Games this season", season_wins, sep = " ") `
 
 `r paste(Total, "predictions this week", sep = " ") `

```{r plotting group results, echo=FALSE}
#Previous Weeks
wins = round(c((wk1_wins/g1_n),(wk2_wins/g2_n),(wk3_wins/g3_n), (wk4_wins/g4_n), (wk5_wins/g5_n),
               (wk6_wins/g6_n),(wk7_wins/g7_n),(wk8_wins/g8_n), (wk9_wins/g9_n), weekly_win_percentage),4)
weeks = c("Week 1", "Week 2", "Week 3", "Week 4", "Week 5", "Week 6", "Week 7", "Week 8", "Week 9",
          "Week_10")
df = as.data.frame(wins, weeks)

ggplot(df, aes(x = weeks, y = wins, group = 1))+
  geom_point()+
  geom_line()+
  geom_text(aes(label=wins),hjust=0, vjust=-1.5)+
  ylim(c(0, 1)) +
  xlab("NFL Week") + 
  ylab("Correct Percentage")+
  ggtitle("Weekly Group Correct Percentage")+
  theme_classic()
```

## Individual Predictions

```{r wk1 individual, include=FALSE}
# Calculating Week 1 Individual Results
indiv_wk1 = week_1 %>% janitor::clean_names() %>%
  select(name, starts_with("game")) 

# Week 1 Individual Results
games_wk1 = indiv_wk1 %>%
  select(-name)

indiv_correct_wk1 = NULL
help_wk1 = NULL
for (i in 1:length(indiv_wk1$name)){
  for(j in 1:length(games_wk1)){
    help_wk1[j] = ifelse(games_wk1[i,j]==wk1_winners[j],1,0)
  indiv_correct_wk1[i] = sum(help_wk1)
  }
}

# Calculating individual win number for week 1
season_wk1 = indiv_wk1 %>%
  select(name) %>%
  add_column(Week_1 = indiv_correct_wk1)

season = season_wk1

# Calculating Week 2 Individual Results
indiv_wk2 = week_2 %>% janitor::clean_names() %>%
  select(name, starts_with("game")) 

games_wk2 = indiv_wk2 %>%
  select(-name)  #Creating the set of just games

indiv_correct_wk2 = NULL
help_wk2 = NULL
for (i in 1:length(indiv_wk2$name)){
  for(j in 1:length(games_wk2)){
    help_wk2[j] = ifelse(games_wk2[i,j]==wk2_winners[j],1,0)
  indiv_correct_wk2[i] = sum(help_wk2)
  }
}

# Calculating individual win number for week 2
season_wk2 = indiv_wk2 %>%
  select(name) %>%
  add_column(Week_2 = indiv_correct_wk2)

# Adding week 2 results to week 1 
season = season %>%
  full_join(season_wk2)

# Calculating Week 3 Individual Results
indiv_wk3 = week_3 %>% janitor::clean_names() %>%
  select(name, starts_with("game")) 

games_wk3 = indiv_wk3 %>%
  select(-name)  #Creating the set of just games

indiv_correct_wk3 = NULL
help_wk3 = NULL
for (i in 1:length(indiv_wk3$name)){
  for(j in 1:length(games_wk3)){
    help_wk3[j] = ifelse(games_wk3[i,j]==wk3_winners[j],1,0)
  indiv_correct_wk3[i] = sum(help_wk3)
  }
}

# Calculating individual win number for week 3
season_wk3 = indiv_wk3 %>%
  select(name) %>%
  add_column(Week_3 = indiv_correct_wk3)

# Adding week 3 to week 1 and 2 
season = season %>%
  full_join(season_wk3)

# Calculating Week 4 Individual Results
indiv_wk4 = week_4 %>% janitor::clean_names() %>%
  select(name, starts_with("game")) 

games_wk4 = indiv_wk4 %>%
  select(-name)  #Creating the set of just games

indiv_correct_wk4 = NULL
help_wk4 = NULL
for (i in 1:length(indiv_wk4$name)){
  for(j in 1:length(games_wk4)){
    help_wk4[j] = ifelse(games_wk4[i,j]==wk4_winners[j],1,0)
  indiv_correct_wk4[i] = sum(help_wk4)
  }
}

# Calculating individual win number for week 4
season_wk4 = indiv_wk4 %>%
  select(name) %>%
  add_column(Week_4 = indiv_correct_wk4)

# Adding week 4 to week 1-3
season = season %>%
  full_join(season_wk4)

# Calculating Week 5 Individual Results
indiv_wk5 = week_5 %>% janitor::clean_names() %>%
  select(name, starts_with("game"))

games_wk5 = indiv_wk5 %>%
  select(-name)  #Creating the set of just games

indiv_correct_wk5 = NULL
help_wk5 = NULL
for (i in 1:length(indiv_wk5$name)){
  for(j in 1:length(games_wk5)){
    help_wk5[j] = ifelse(games_wk5[i,j]==wk5_winners[j],1,0)
  indiv_correct_wk5[i] = sum(help_wk5)
  }
}

# Calculating individual win number for week 5
season_wk5 = indiv_wk5 %>%
  select(name) %>%
  add_column(Week_5 = indiv_correct_wk5)

# Adding week 5 to week 1-4
season = season %>%
  full_join(season_wk5)

# Calculating Week 6 Individual Results
indiv_wk6 = week_6 %>% janitor::clean_names() %>%
  select(name, starts_with("game"))

games_wk6 = indiv_wk6 %>%
  select(-name)  #Creating the set of just games

indiv_correct_wk6 = NULL
help_wk6 = NULL
for (i in 1:length(indiv_wk6$name)){
  for(j in 1:length(games_wk6)){
    help_wk6[j] = ifelse(games_wk6[i,j]==wk6_winners[j],1,0)
  indiv_correct_wk6[i] = sum(help_wk6)
  }
}

# Calculating individual win number for week 6
season_wk6 = indiv_wk6 %>%
  select(name) %>%
  add_column(Week_6 = indiv_correct_wk6)

# Adding week 6 to week 1-5
season = season %>%
  full_join(season_wk6)

# Calculating Week 7 Individual Results
indiv_wk7 = week_7 %>% janitor::clean_names() %>%
  select(name, starts_with("game"))

games_wk7 = indiv_wk7 %>%
  select(-name)  #Creating the set of just games

indiv_correct_wk7 = NULL
help_wk7 = NULL
for (i in 1:length(indiv_wk7$name)){
  for(j in 1:length(games_wk7)){
    help_wk7[j] = ifelse(games_wk7[i,j]==wk7_winners[j],1,0)
  indiv_correct_wk7[i] = sum(help_wk7)
  }
}

# Calculating individual win number for week 7
season_wk7 = indiv_wk7 %>%
  select(name) %>%
  add_column(Week_7 = indiv_correct_wk7)

# Adding week 7 to week 1-6
season = season %>%
  full_join(season_wk7)

# Calculating Week 8 Individual Results
indiv_wk8 = week_8 %>% janitor::clean_names() %>%
  select(name, starts_with("game"))

games_wk8 = indiv_wk8 %>%
  select(-name)  #Creating the set of just games

indiv_correct_wk8 = NULL
help_wk8 = NULL
for (i in 1:length(indiv_wk8$name)){
  for(j in 1:length(games_wk8)){
    help_wk8[j] = ifelse(games_wk8[i,j]==wk8_winners[j],1,0)
  indiv_correct_wk8[i] = sum(help_wk8)
  }
}

# Calculating individual win number for week 8
season_wk8 = indiv_wk8 %>%
  select(name) %>%
  add_column(Week_8 = indiv_correct_wk8)

# Adding week 8 to week 1-7
season = season %>%
  full_join(season_wk8)

# Calculating Week 9 Individual Results
indiv_wk9 = week_9 %>% janitor::clean_names() %>%
  select(name, starts_with("game"))

games_wk9 = indiv_wk9 %>%
  select(-name)  #Creating the set of just games

indiv_correct_wk9 = NULL
help_wk9 = NULL
for (i in 1:length(indiv_wk9$name)){
  for(j in 1:length(games_wk9)){
    help_wk9[j] = ifelse(games_wk9[i,j]==wk9_winners[j],1,0)
  indiv_correct_wk9[i] = sum(help_wk9)
  }
}

# Calculating individual win number for week 9
season_wk9 = indiv_wk9 %>%
  select(name) %>%
  add_column(Week_9 = indiv_correct_wk9)

# Adding week 9 to week 1-8
season = season %>%
  full_join(season_wk9)
```

```{r individual, include=FALSE}
# Creating the set of names and games

indiv = data %>% janitor::clean_names() %>%
  select(name, starts_with("game"))

# Counting the correct number of pics for each person  

indiv_correct = NULL
help = NULL
for (i in 1:length(indiv$name)){
  for(j in 1:length(games)){
    help[j] = ifelse(games[i,j]==winners[j],1,0)
  indiv_correct[i] = sum(help)
  }
}

# Calculating individual win percentage, combining data and orderign by percentage 
indiv = indiv %>% 
  add_column(WK10_Correct = indiv_correct) %>%
  mutate(WK10_Percent = round(WK10_Correct/n,4)) %>%
  rename("Week_10" = WK10_Correct)%>%
  rename("Percent" = WK10_Percent)%>%
  arrange(-Percent)

# choosing just name # correct pics and correct percentage
indiv_disp = indiv %>%
  select(name, Week_10, Percent) %>%
  full_join(season) %>%
  mutate(w1p = ifelse(is.na(Week_1)==T,0,1)) %>%
  mutate(w2p = ifelse(is.na(Week_2)==T,0,1)) %>%
  mutate(w3p = ifelse(is.na(Week_3)==T,0,1)) %>%
  mutate(w4p = ifelse(is.na(Week_4)==T,0,1)) %>%
  mutate(w5p = ifelse(is.na(Week_5)==T,0,1)) %>%
  mutate(w6p = ifelse(is.na(Week_6)==T,0,1)) %>%
  mutate(w7p = ifelse(is.na(Week_7)==T,0,1)) %>%
  mutate(w8p = ifelse(is.na(Week_8)==T,0,1)) %>%
  mutate(w9p = ifelse(is.na(Week_9)==T,0,1)) %>%
  mutate(w10p = ifelse(is.na(Week_10)==T,0,1)) %>%
  mutate(Weeks_Picked = w1p+w2p+w3p+w4p+w5p+w6p+w7p+w8p+w9p+w10p) %>%
  mutate(games_picked = ((w1p*wk1_n)+(w2p*wk2_n)+(w3p*wk3_n)+(w4p*wk4_n)+(w5p*wk5_n)+
                           (w6p*wk6_n)+(w7p*wk7_n)+(w8p*wk8_n)+(w9p*wk9_n)+(w10p*n))) %>%
  mutate(Season_Percent = round(((ifelse(is.na(Week_1)==T, 0, Week_1) + 
                             ifelse(is.na(Week_2)==T,0,Week_2) +
                             ifelse(is.na(Week_3)==T,0,Week_3)+
                             ifelse(is.na(Week_4)==T,0,Week_4)+
                             ifelse(is.na(Week_5)==T,0,Week_5)+
                             ifelse(is.na(Week_6)==T,0,Week_6)+
                             ifelse(is.na(Week_7)==T,0,Week_7)+
                             ifelse(is.na(Week_8)==T,0,Week_8)+
                             ifelse(is.na(Week_9)==T,0,Week_9)+
                             ifelse(is.na(Week_10)==T,0,Week_10))/games_picked),4)) %>%
  select(name, Week_1, Week_2, Week_3, Week_4, Week_5, Week_6, Week_7, Week_8, Week_9, Week_10, 
         Percent, Weeks_Picked, Season_Percent) %>%
  arrange(desc(Percent), desc(Season_Percent)) %>%
  mutate(Adj_Season_Percent = round(Season_Percent*(Weeks_Picked/max(Weeks_Picked)),4))

#formating chart for stars 
improvement_formatter <- 
  formatter("span", 
            style = x ~ style(
              font.weight = "bold", 
              color = ifelse(x > .5, "green", ifelse(x < .5, "red", "black"))),
             x ~ icontext(ifelse(x == max(x), "star", ""), x))

improvement_formatter3 <- 
  formatter("span", 
            style = x ~ style(
              font.weight = "bold", 
              color = ifelse(x > .5, "green", ifelse(x < .5, "red", "black"))),
             x ~ icontext(ifelse(x == x[1], "star", ""), x))

# Creating individual results table
Week_10_indiv = formattable(indiv_disp,
            align =c("l","c","c", "c", "c", "c", "c","c","c", "c", "c", "c","c","c", "c"), 
            list(
              `Indicator Name` = formatter("span", 
                                style = ~ style(color = "grey",font.weight = "bold")),
              "Percent" = improvement_formatter3, 
              "Season_Percent" = improvement_formatter,
              "Adj_Season_Percent" = improvement_formatter
              
))
```

```{r individual Display, echo=FALSE}
# Printing the individual table 
Week_10_indiv

indi = indiv_disp %>% 
  select(name, Week_1, Week_2, Week_3, Week_4, Week_5, Week_6, Week_7, Week_8, Week_9, Percent) %>%
  mutate(Week_1 = Week_1/(wk1_n))%>%
  mutate(Week_2 = Week_2/(wk2_n))%>%
  mutate(Week_3 = Week_3/(wk3_n))%>%
  mutate(Week_4 = Week_4/(wk4_n))%>%
  mutate(Week_5 = Week_5/(wk5_n))%>%
  mutate(Week_6 = Week_6/(wk6_n))%>%
  mutate(Week_7 = Week_7/(wk7_n))%>%
  mutate(Week_8 = Week_8/(wk8_n))%>%
  mutate(Week_9 = Week_9/(wk9_n))%>%
  as.data.frame()
na = rep(indi$name, 10)
we1 = c(indi$Week_1,indi$Week_2,indi$Week_3,indi$Week_4, indi$Week_5, indi$Week_6, indi$Week_7, indi$Week_8, indi$Week_9, indi$Percent)
we2 = c(rep("Week 1", length(indi$name)), rep("Week 2", length(indi$name)),
        rep("Week 3", length(indi$name)), rep("Week 4", length(indi$name)),
        rep("Week 5", length(indi$name)), rep("Week 6", length(indi$name)),
        rep("Week 7", length(indi$name)), rep("Week 8", length(indi$name)),
        rep("Week 9", length(indi$name)), rep("Week 10", length(indi$name)))
i_df = cbind.data.frame(na, we1, we2)

ggplot(i_df, aes(x = we2, y = we1, group = na, color = na))+
  geom_point()+
  geom_line()+
  geom_text_repel(aes(label=na),hjust=0, vjust=0)+
  ylim(c(0, 1)) +
  xlab("NFL Week") + 
  ylab("Correct Percentage")+
  ggtitle("Weekly Individual Correct Percentage")+
  theme_classic()

```

## Combined Cadet and Instructor Prediction 

```{r combined, echo=FALSE}
##comvined cadet and instructor prediction
c_games = cadet_wk10%>% janitor::clean_names() %>%
  select(starts_with("game"))  #Creating the set of just games

tot_games = rbind(games, c_games)
# creating a table of predictions and votes for and against the prediction
t_pred_table = data.frame(Game=colnames(tot_games), 
                        t(sapply(tot_games, # apply following function to each column
                                 function(x) {
                                   t_x <- sort(table(x), decreasing=TRUE) # get the frequencies and sort them in decreasing order
                                   list(Prediction=names(t_x)[1], # name of the value with highest frequency
                                        votes_for=t_x[1], # highest frequency
                                        votes_against=t_x[2]) # Lowest Freq
                                 })))

#establish vectors for precictions and votes for and against
t_pred = as.character(t_pred_table$Prediction)
t_votes_for = ifelse(is.na(t_pred_table$votes_for)==T, 0, as.integer(t_pred_table$votes_for))
t_votes_against = ifelse(is.na(t_pred_table$votes_against)==T, 0, as.integer(t_pred_table$votes_against))

total = tibble(Game = 1:length(games)) %>% 
  add_column(Total_Prediction = t_pred) %>%
  add_column(Winners = winners) %>%
  mutate(Correct = ifelse(Total_Prediction == winners, "Yes", "No")) %>%
  mutate(Correct_Votes = ifelse(Total_Prediction == winners, t_votes_for, 
                                ifelse(winners == "TIE", 0, t_votes_against))) %>%
  mutate(Percentage_For = round(Correct_Votes/dim(tot_games)[1],4)) %>%
  rename("Correct Votes" = Correct_Votes) %>%
  rename("Correct Percent" = Percentage_For) %>%
  rename("Total Prediction" = Total_Prediction)

# Creatign Group Prediction table            
formattable(total, 
            align =c("c","c","c"), 
            list(
              `Indicator Name` = formatter("span", 
                                style = ~ style(color = "grey",font.weight = "bold")),
                                "Correct" = improvement_formatter2))

t_correct_count = count(total, Correct)
t_weekly_win_percentage = round(t_correct_count$n[which(t_correct_count$Correct == "Yes")]/n,4)
tot_pickers = dim(data)[1] + dim(cadet_wk10)[1]
```
`r paste("Our win percentage for combined predictions is", t_weekly_win_percentage, sep = " ") `

`r paste(tot_pickers, "total predictions this week", sep = " ") `

```{r combined plot, echo=FALSE}
c_wins = round(c((wk1_combined_wins/wk1_n), (wk2_combined_wins/wk2_n),(wk3_combined_wins/wk3_n),
           (wk4_combined_wins/wk4_n), (wk5_combined_wins/wk5_n), (wk6_combined_wins/wk6_n),
           (wk7_combined_wins/wk7_n), (wk8_combined_wins/wk8_n), (wk9_combined_wins/wk9_n),
           t_weekly_win_percentage), 4)
c_df = as.data.frame(c_wins, weeks)

ggplot(c_df, aes(x = weeks, y = c_wins, group = 1))+
  geom_point()+
  geom_line()+
  geom_text(aes(label=c_wins),hjust=0, vjust=-1.5)+
  ylim(c(0, 1)) +
  xlab("NFL Week") + 
  ylab("Correct Percentage")+
  ggtitle("Weekly Combined Correct Percentage")+
  theme_classic()
```

## Results where cadet and instructor predictions match

```{r matched week 2, echo=FALSE}
#### Che checking the win percentage where instructor and cadet predictions match 
c_games = cadet_wk10 %>% janitor::clean_names() %>%
  select(starts_with("game"))  #Creating the set of just games

# creating a table of predictions and votes for and against the prediction
c_pred_table = data.frame(Game=colnames(c_games), 
                        t(sapply(c_games, # apply following function to each column
                                 function(x) {
                                   t_x <- sort(table(x), decreasing=TRUE) # get the frequencies and sort them in decreasing order
                                   list(Prediction=names(t_x)[1], # name of the value with highest frequency
                                        votes_for=t_x[1], # highest frequency
                                        votes_against=t_x[2]) # Lowest Freq
                                 })))

#establish vectors for precictions and votes for and against
c_pred = as.character(c_pred_table$Prediction)
c_votes_for = ifelse(is.na(c_pred_table$votes_for)==T, 0, as.integer(c_pred_table$votes_for))
c_votes_against = ifelse(is.na(c_pred_table$votes_against)==T, 0, as.integer(c_pred_table$votes_against))

match = ifelse(pred == c_pred, pred, "No")

matched = tibble(Game = 1:length(games)) %>% 
  add_column(Matched_Prediction = match) %>%
  mutate(Correct = ifelse(match == winners, "Yes", ifelse(match == "No", "--", "No")))

# Creatign Group Prediction table            
formattable(matched, 
            align =c("c","c","c"), 
            list(
              `Indicator Name` = formatter("span", 
                                style = ~ style(color = "grey",font.weight = "bold")),
                                "Correct" = improvement_formatter2))

mat = matched %>%
  filter(match != "No") %>%
  group_by(Correct) %>%
  count()

matched_win = round(mat$n[which(mat$Correct == "Yes")]/sum(mat$n),4)
```

`r paste("Matched cadet instructor win percentage this week is", matched_win, sep = " ") `

```{r pregame, eval=FALSE, include=FALSE}
#Predictions for the week
Pregame = tibble(Game = 1:length(games)) %>% 
  add_column(Prediction = pred)

pre_game = formattable(Pregame,
            align =c("c","c", "c"), 
            list(
              `Indicator Name` = formatter("span", 
                                style = ~ style(color = "grey",font.weight = "bold"))))
pre_game

library(usethis)
use_git_config(user.name = "Daniel Baller", user.email = "danballer13@gmail.com")
```
