---
title: "NFL Week 12 MA206, 2019"
author: "MAJ Daniel Baller"
date: "11/19/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = F)
library(tidyverse)
library(dplyr)
library(ggplot2)
library(data.table)
library(formattable)
library(ggpubr)
library(ggrepel)
# week_1 = read_csv("NFL Week 1.csv")
# week_2 = read_csv("NFL Week 2.csv")
# week_3 = read_csv("NFL Week 3.csv")
# week_4 = read_csv("NFL Week 4.csv")
# week_5 = read_csv("NFL Week 5.csv")
# week_6 = read_csv("NFL Week 6.csv")
# week_7 = read_csv("NFL Week 7.csv")
# week_8 = read_csv("NFL Week 8.csv")
# week_9 = read_csv("NFL Week 9.csv")
# week_10 = read_csv("NFL Week 10.csv")
# week_11 = read_csv("NFL Week 11.csv") # Update
# data = read_csv("NFL Week 12.csv") # Update
week_1 = read_csv("NFL Week 1 MA206.csv")
week_2 = read_csv("NFL Week 2 MA206.csv")
week_3 = read_csv("NFL Week 3 MA206.csv")
week_4 = read_csv("NFL Week 4 MA206.csv")
week_5 = read_csv("NFL Week 5 MA206.csv")
week_6 = read_csv("NFL Week 6 MA206.csv")
week_7 = read_csv("NFL Week 7 MA206.csv") 
week_8 = read_csv("NFL Week 8 MA206.csv") 
week_9 = read_csv("NFL Week 9 MA206.csv") 
week_10 = read_csv("NFL Week 10 MA206.csv")
week_11 = read_csv("NFL Week 11 MA206.csv")
data = read_csv("NFL Week 12 MA206.csv") # Update
```

```{r games, include=FALSE}
#basic info

n = 14 #number of games this week
wk1_n = 16 # number of games in week 1
wk2_n = 16 # number of games in week 2
wk3_n = 16 # number of games in week 3
wk4_n = 15 # number of games in week 4
wk5_n = 15 # number of games in week 5
wk6_n = 13 # number of games in week 6
wk7_n = 14 # number of games in week 7
wk8_n = 15 # number of games in week 8
wk9_n = 14 # number of games in week 9
wk10_n = 13 # number of games in week 10
wk11_n = 14 # number of games in week 11
wk_max = c(wk1_n, wk2_n, wk3_n, wk4_n, wk5_n, wk6_n, wk7_n, wk8_n, wk9_n, wk10_n, wk11_n, n)
g1_n = 16 # number of group picks in week 1
g2_n = 16 # number of group picks in week 2
g3_n = 16 # number of group picks in week 3
g4_n = 15 # number of group picks in week 4
g5_n = 15 # number of group picks in week 5
g6_n = 13 # number of group picks in week 6
g7_n = 14 # number of group picks in week 7
g8_n = 15 # number of group picks in week 8
g9_n = 14 # number of group picks in week 9
g10_n = 13 # number of group picks in week 10
g11_n = 14 # number of group picks in week 11

wk1_wins = 10 #number of wins in week 1
wk2_wins = 10 #number of wins in week 2
wk3_wins = 12 #number of wins in week 3
wk4_wins = 8 #number of wins in week 4 
wk5_wins = 8 #number of wins in week 5 
wk6_wins = 7 #number of wins in week 6 
wk7_wins = 9 #number of wins in week 7 
wk8_wins = 13 #number of wins in week 8 
wk9_wins = 7 #number of wins in week 9
wk10_wins = 5 #number of wins in week 10
wk11_wins = 12 #number of wins in week 11 #update this

wk1_combined_wins = 12 # number of combined wins in week 1
wk2_combined_wins = 10 # number of combined wins in week 2
wk3_combined_wins = 10 # number of combined wins in week 3 
wk4_combined_wins = 8 # number of combined wins in week 4 
wk5_combined_wins = 9 # number of combined wins in week 5 
wk6_combined_wins = 7 # number of combined wins in week 6 
wk7_combined_wins = 10 # number of combined wins in week 7 
wk8_combined_wins = 13 # number of combined wins in week 8
wk9_combined_wins = 7 # number of combined wins in week 9 
wk10_combined_wins = 3 # number of combined wins in week 10 # update this
wk11_combined_wins = 12 # number of combined wins in week 11 # update this

# who actually won
winners = c("Houston Texans","Buffalo Bills", "Chicago Bears", "Pittsburgh Steelers","Cleveland Browns", "Tampa Bay Buccaneers","New Orleans Saints","Seattle Seahawks","Washington Redskins","New York Jets","Tennessee Titans","New England Patriots","San Francisco 49ers","Baltimore Ravens")

CBSsports = c("Houston Texans","Buffalo Bills", "Chicago Bears", "Pittsburgh Steelers","Cleveland Browns", "Atlanta Falcons","New Orleans Saints","Philadelphia Eagles","Detroit Lions","Oakland Raiders","Jacksonville Jaguars","New England Patriots","Green Bay Packers","Baltimore Ravens")


experts = ifelse(winners == CBSsports, 1, 0)
CBS = round(sum(experts)/n,4)

#### Previous Weeks Winners #####
wk1_winners = c("Green Bay Packers","Minnesota Vikings","Baltimore Ravens","Buffalo Bills","Kansas City Chiefs","Los Angeles Rams","Tennessee Titans","Philadelphia Eagles","Seattle Seahawks","Los Angeles Chargers","TIE","Dallas Cowboys","San Francisco 49ers","New England Patriots","New Orleans Saints","Oakland Raiders")

wk2_winners = c("Tampa Bay Buccaneers","Baltimore Ravens","Dallas Cowboys","Indianapolis Colts","Seattle Seahawks","Buffalo Bills","San Fransisco 49ers","Detroit Lions","Green Bay Packers","Houston Texans","New England Patriots","Kansas City Chiefs","Los Angeles Rams","Chicago Bears","Atlanta Falcons","Cleveland Browns")

wk3_winners = c("Jacksonville Jaguars","Buffalo Bills","Detroit Lions","New England Patriots","Minnesota Vikings","Kansas City Chiefs","Indianapolis Colts","Green Bay Packers","Dallas Cowboys","New York Giants","Carolina Panthers","San Francisco 49ers","New Orleans Saints","Houston Texans","Los Angeles Rams","Chicago Bears") 

wk4_winners = c("Philadelphia Eagles","Tennessee Titans","New York Giants","Los Angeles Chargers","Oakland Raiders","Carolina Panthers","Kansas City Chiefs","Cleveland Browns","New England Patriots","Tampa Bay Buccaneers","Seattle Seahawks","Chicago Bears","Jacksonville Jaguars","New Orleans Saints","Pittsburgh Steelers")

wk5_winners = c("Seattle Seahawks","Carolina Panthers","New England Patriots","Buffalo Bills","Baltimore Ravens","Arizona Cardinals","Houston Texans","New Orleans Saints","Minnesota Vikings","Oakland Raiders","Philadelphia Eagles","Denver Broncos","Green Bay Packers","Indianapolis Colts","San Francisco 49ers") 

wk6_winners = c("New England Patriots","Carolina Panthers","Washington Redskins","Minnesota Vikings","Houston Texans","New Orleans Saints","Seattle Seahawks","San Francisco 49ers","Arizona Cardinals","New York Jets","Denver Broncos","Pittsburgh Steelers","Green Bay Packers") 

wk7_winners = c("Kansas City Chiefs","Buffalo Bills","Jacksonville Jaguars","Minnesota Vikings","Green Bay Packers","Los Angeles Rams","Indianapolis Colts","San Francisco 49ers","Arizona Cardinals","Tennessee Titans","New Orleans Saints","Baltimore Ravens","Dallas Cowboys","New England Patriots")

wk8_winners = c("Minnesota Vikings","Seattle Seahawks","Indianapolis Colts","Tennessee Titans","New Orleans Saints","Los Angeles Rams","Philadelphia Eagles","Los Angeles Chargers","Detroit Lions","Jacksonville Jaguars","San Francisco 49ers","Houston Texans","New England Patriots","Green Bay Packers","Pittsburgh Steelers")

wk9_winners = c("San Francisco 49ers","Houston Texans", "Philadelphia Eagles","Pittsburgh Steelers","Miami Dolphins","Kansas City Chiefs","Carolina Panthers","Buffalo Bills","Seattle Seahawks","Oakland Raiders","Los Angeles Chargers","Denver Broncos","Baltimore Ravens","Dallas Cowboys") 

wk10_winners = c("Oakland Raiders","Baltimore Ravens","Cleveland Browns","Chicago Bears","New York Jets","Tennessee Titans","Tampa Bay Buccaneers","Atlanta Falcons","Miami Dolphins","Pittsburgh Steelers","Green Bay Packers","Minnesota Vikings","Seattle Seahawks")

wk11_winners = c("Cleveland Browns","Atlanta Falcons", "Dallas Cowboys","Indianapolis Colts","Buffalo Bills","Baltimore Ravens","Minnesota Vikings","New York Jets","New Orleans Saints","San Francisco 49ers","Oakland Raiders","New England Patriots","Los Angeles Rams","Kansas City Chiefs")
```

```{r Group Historical CBS, include=FALSE}
#wk1_CBSsports = c("Green Bay Packers","Atlanta Falcons","Miami Dolphins","New York Jets","Kansas City Chiefs","Carolina Panthers","Cleveland Browns","Philadelphia Eagles","Seattle Seahawks","Indianapolis Colts","Arizona Cardinals","Dallas Cowboys","Tampa Bay Buccaneers","Pittsburgh Steelers","New Orleans Saints","Oakland Raiders")

#wk2_CBSsports = c("Carolina Panthers","Baltimore Ravens","Dallas Cowboys","Indianapolis Colts","Seattle Seahawks","Buffalo Bills","Cincinnati Bengals","Los Angeles Chargers","Green Bay Packers","Houston Texans","New England Patriots","Kansas City Chiefs","Los Angeles Rams","Chicago Bears","Philadelphia Eagles","Cleveland Browns")

#wk3_CBSsports = c("Jacksonville Jaguars","Buffalo Bills","Philidelphia Eagles","New England Patriots","Minnesota Vikings","Baltimore Ravens","Atlanta Falcons","Green Bay Packers","Dallas Cowboys","Tampa Bay Buccaneers","Carolina Panthers","San Francisco 49ers","Seattle Seahawks","Los Angeles Chargers","Los Angeles Rams","Chicago Bears") 

#wk4_CBSsports = c("Green Bay Packers","Atlanta Falcons","Washington Redskins","Los Angeles Chargers","Indianapolis Colts","Carolina Panthers","Kansas City Chiefs","Baltimore Ravens","New England Patriots","Los Angeles Rams","Seattle Seahawks","Chicago Bears","Jacksonville Jaguars","Dallas Cowboys","Pittsburgh Steelers")

#Wk5_CBSsports = c("Seattle Seahawks","Jacksonville Jaguars","New England Patriots","Tennessee Titans","Baltimore Ravens","Cincinnati Bangals","Houston Texans","Tamps Bay Buccaneers","Minnesota Vikings","Chicago Bears","Philadelphia Eagles","Los Angeles Chargers","Dallas Cowboys","Kansas City Chiefs","Cleveland Browns")

#wk6_CBSsports = c("New England Patriots","Tampa Bay Buccaneers","Washington Redskins","Philadelphia Eagles","Kansas City Chiefs","New Orleans Saints","Seattle Seahawks","San Francisco 49ers","Atlanta Falcons","Dallas Cowboys","Tennessee Titans","Los Angeles Chargers","Green Bay Packers")

#wk7_CBSsports = c("Denver Broncos","Buffalo Bills", "Jacksonville Jaguars","Minnesota Vikings","Green Bay Packers","Los Angeles Rams","Houston Texans","San Francisco 49ers","Arizona Cardinals","Los Angeles Chargers","New Orleans Saints","Baltimore Ravens","Philadelphia Eagless","New England Patriots")

#wk8_CBSsports = c("Minnesota Vikings","Seattle Seahawks","Indianapolis Colts","Tampa Bay Buccaneers","New Orleans Saints","Los Angeles Rams","Philadelphia Eagles","Los Angeles Chargers","Detroit Lions","Jacksonville Jaguars","San Francisco 49ers","Houston Texans","New England Patriots","Green Bay Packers","Pittsburgh Steelers")

#wk9_CBSsports = c("San Francisco 49ers","Houston Texans", "Philadelphia Eagles","Indianapolis Colts","New York Jets","Minnesota Vikings","Carolina Panthers","Buffalo Bills","Seattle Seahawks","Oakland Raiders","Green Bay Packers","Cleveland Browns","Baltimore Ravens","Dallas Cowboys")

#wk10_CPSsports = c("Oakland Raiders","Baltimore Ravens","Buffalo Bills","Detroit Lions","New York Giants","Kansas City Chiefs","Tampa Bay Buccaneers","New Orleans Saints","Indianapolis Colts","Los Angeles Rams","Green Bay Packers","Minnesota Vikings","Seattle Seahawks")

#wk11_CBSsports = c("Pittsburgh Steelers","Carolina Panthers", "Dallas Cowboys","Jacksonville Jaguars","Buffalo Bills","Baltimore Ravens","Minnesota Vikings","New York Jets","New Orleans Saints","San Francisco 49ers","Oakland Raiders","Philadelphia Eagles","Los Angeles Rams","Kansas City Chiefs")
```

## Group Predictions

```{r Group Predictions, include=FALSE}
games = data %>% janitor::clean_names() %>%
  select(starts_with("game"))  #Creating the set of just games

# creating a table of predictions and votes for and against the prediction
pred_table = data.frame(Game=colnames(games), 
                        t(sapply(games, # apply following function to each column
                                 function(x) {
                                   t_x <- sort(table(x), decreasing=TRUE) # get the frequencies and sort them in decreasing order
                                   list(Prediction=names(t_x)[1], # name of the value with highest frequency
                                        votes_for=t_x[1], # highest frequency
                                        votes_against=t_x[2]) # Lowest Freq
                                 })))

#establish vectors for precictions and votes for and against
pred_table = pred_table %>% 
  mutate(votes_against = ifelse(is.na(pred_table$votes_against)==T, 0, as.integer(pred_table$votes_against))) # turning NA in votes against column into 0
pred = ifelse(as.numeric(pred_table$votes_for) == as.numeric(pred_table$votes_against), "Tie", as.character(pred_table$Prediction)) #choosing prediction or tie if no prediction
#votes_for = ifelse(is.na(pred_table$votes_for)==T, 0, as.integer(pred_table$votes_for))
votes_for = as.integer(pred_table$votes_for)
votes_against = as.integer(pred_table$votes_against)

results = tibble(Game = 1:length(games)) %>% 
  add_column(Prediction = pred) %>%
  add_column(Winners = winners) %>%
  mutate(Correct = ifelse(Prediction =="Tie", "--", ifelse(Prediction == Winners, "Yes", "No"))) %>%
  mutate(Correct_Votes = ifelse(Prediction == winners, votes_for, ifelse(winners == "TIE", 0, votes_against))) %>%
  mutate(Percentage_For = round(Correct_Votes/dim(data)[1],4)) %>%
  rename("Correct Votes" = Correct_Votes) %>%
  rename("Correct Percent" = Percentage_For)
results
```

```{r displaying group results, echo=FALSE}
# formating for color of table
improvement_formatter2 <- 
  formatter("span", 
            style = x ~ style(
              font.weight = "bold", 
              color = ifelse(x == "Yes", "green", ifelse(x =="No", "red", "black"))))


# Creatign Group Prediction table            
formattable(results, 
            align =c("c","c","c"), 
            list(
              `Indicator Name` = formatter("span", 
                                style = ~ style(color = "grey",font.weight = "bold")),
                                "Correct" = improvement_formatter2))

# Printing the weekly and season win percentage            
correct_count = count(results, Correct)
weekly_win_percentage = round(correct_count$n[which(correct_count$Correct == "Yes")]/(n-ifelse(identical(correct_count$n[which(correct_count$Correct == "--")], integer(0))==TRUE, 0, correct_count$n[which(correct_count$Correct == "--")])),4)
group_games = (n-ifelse(identical(correct_count$n[which(correct_count$Correct == "--")], integer(0))==TRUE, 0, correct_count$n[which(correct_count$Correct == "--")]))
season_games = group_games+g1_n+g2_n+g3_n+g4_n+g5_n+g6_n+g7_n+g8_n+g9_n+g10_n+g11_n
season_wins  = wk1_wins+wk2_wins+wk3_wins+wk4_wins+wk5_wins+wk6_wins+wk7_wins+wk8_wins+wk9_wins+
  wk10_wins+wk11_wins+correct_count$n[which(correct_count$Correct == "Yes")]
season_win_percentage = round(season_wins/(season_games),4)
Total = dim(data)[1]
```
 `r paste("Our win percentage for the week is", weekly_win_percentage, sep = " ") `
 
 `r paste("CBS Sports win percentage for the week is", CBS, sep = " ") `
 
 `r paste("Our season win percentage so far is", season_win_percentage, sep = " ") `
 
 `r paste("Games picked this season", season_games, sep = " ") `
 
 `r paste("Correct Games this season", season_wins, sep = " ") `
 
 `r paste(Total, "predictions this week", sep = " ") `

```{r plotting group results, echo=FALSE}
#Previous Weeks
wins = round(c((wk1_wins/g1_n),(wk2_wins/g2_n),(wk3_wins/g3_n), (wk4_wins/g4_n), (wk5_wins/g5_n),
               (wk6_wins/g6_n),(wk7_wins/g7_n),(wk8_wins/g8_n), (wk9_wins/g9_n),
               (wk10_wins/g10_n),(wk11_wins/g11_n),  weekly_win_percentage),4)
weeks = c("Week 1", "Week 2", "Week 3", "Week 4", "Week 5", "Week 6", "Week 7", "Week 8", "Week 9",
          "Week_10", "Week_11", "Week_12")
df = as.data.frame(wins, weeks)

ggplot(df, aes(x = weeks, y = wins, group = 1))+
  geom_point()+
  geom_line()+
  geom_text(aes(label=wins),hjust=0, vjust=-1.5)+
  ylim(c(0, 1)) +
  xlab("NFL Week") + 
  ylab("Correct Percentage")+
  ggtitle("Weekly Group Correct Percentage")+
  theme_classic()
```

## Individual Predictions

```{r individual correct over season, include=FALSE}
############# Creating a function to calculate weekly correct picks #############

indiv_weekly_pred = function(x,y){
indiv = x %>% janitor::clean_names() %>%
  select(name, starts_with("game")) 

games_wk = indiv %>%
  select(-name)

indiv_correct_wk = NULL
help = NULL
for (i in 1:length(indiv$name)){
  for(j in 1:length(games_wk)){
    help[j] = ifelse(games_wk[i,j]==y[j],1,0)
    indiv_correct_wk[i] = sum(help)
  }
}
season_wk = indiv %>%
  select(name) %>%
  add_column(Week = indiv_correct_wk)
return(season_wk)
}
###############################################################
######### Weekly Individual Correct Picks #####################
###############################################################

#Calculating weekly correct pics for each person
season = indiv_weekly_pred(week_1, wk1_winners) %>%
  rename("Week_1" = Week)%>%
  full_join(indiv_weekly_pred(week_2, wk2_winners) %>%
      rename("Week_2" = Week))%>%
  full_join(indiv_weekly_pred(week_3, wk3_winners) %>%
      rename("Week_3" = Week)) %>%
  full_join(indiv_weekly_pred(week_4, wk4_winners) %>%
      rename("Week_4" = Week)) %>%
  full_join(indiv_weekly_pred(week_5, wk5_winners) %>%
      rename("Week_5" = Week)) %>%
  full_join(indiv_weekly_pred(week_6, wk6_winners) %>%
      rename("Week_6" = Week)) %>%
  full_join(indiv_weekly_pred(week_7, wk7_winners) %>%
      rename("Week_7" = Week)) %>%
  full_join(indiv_weekly_pred(week_8, wk8_winners) %>%
      rename("Week_8" = Week)) %>%
  full_join(indiv_weekly_pred(week_9, wk9_winners) %>%
      rename("Week_9" = Week)) %>%
  full_join(indiv_weekly_pred(week_10, wk10_winners) %>%
      rename("Week_10" = Week)) %>%
  full_join(indiv_weekly_pred(week_11, wk11_winners) %>%
      rename("Week_11" = Week)) %>%
  full_join(indiv_weekly_pred(data, winners) %>% ####### Add line for previous week and update to current week
      rename("Week_12" = Week)) %>%
  mutate(Percent = round(Week_12/n,4)) %>%
  arrange(-Percent)

#Creating a dataframe with only the weekly picks
a = season %>% select(-name, -Percent)

#Creating a vector of how many weeks each person picked over the season
tot_week = NULL
help = NULL
for (i in 1:dim(a)[1]){
  for(j in 1:length(a)){
    help[j] = ifelse(is.na(a[i,j])==T,0,1)
    tot_week[i] = sum(help)
  }
}

#Creating a vector of how many games each person picked over the season
tot_picks= NULL
help = NULL
for (i in 1:dim(a)[1]){
  for(j in 1:length(a)){
    help[j] = wk_max[j]*ifelse(is.na(a[i,j])==T,0,1)
    tot_picks[i] = sum(help)
  }
}

#Creatign a vector of how many games each person picked correct over the season
tot_correct = NULL
help = NULL
for (i in 1:dim(a)[1]){
  tot_correct[i] = sum(a[i,], na.rm = T)
}

#adding how many weeks each person picked, season correct percentage, and adjusted season percentag to the data frame and sorting the data
indiv_disp = season %>% add_column(Weeks_Picked = tot_week) %>%
  add_column(tot_correct)%>%
  add_column(tot_picks)%>%
  mutate(Season_Percent = round(tot_correct/tot_picks,4))%>%
  mutate(Adj_Season_Percent=round(Season_Percent*(tot_week/length(a)),4)) %>%
  select(-tot_correct, -tot_picks) %>%
  arrange(desc(Percent), desc(Season_Percent)) %>%
  mutate(Percent = ifelse(is.na(Percent)==T, 0, Percent))
  
```

```{r individual, echo=FALSE}
#formating chart for stars 
improvement_formatter <- 
  formatter("span", 
            style = x ~ style(
              font.weight = "bold", 
              color = ifelse(x > .5, "green", ifelse(x < .5, "red", "black"))),
             x ~ icontext(ifelse(x == max(x), "star", ""), x))

# Creating individual results table
current_indiv = formattable(indiv_disp,
            align =c("l","c","c","c","c","c","c","c","c","c","c","c","c","c","c","c","c"), 
            list(
              `Indicator Name` = formatter("span", 
                                style = ~ style(color = "grey",font.weight = "bold")),
              "Percent" = improvement_formatter, 
              "Season_Percent" = improvement_formatter,
              "Adj_Season_Percent" = improvement_formatter
              
))
current_indiv
```